ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
Edit title and abstract

\documentclass{bioinfo}
\copyrightyear{2021} \pubyear{2021}

@@

    \title[short Title]{ODGI: scalable tools for working with pangenome graphs}
    \author[Sample \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2}}$,
        XXXXX,
        Pjotr Prins\,$^{\text{\sfb 3}}$ and
        Erik Garrison\,$^{\text{\sfb 3,}*}$
    }
    \address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 2}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 3}}$Department, Institution, City, Post Code, Country
    }

@@

    \abstract{
        \textbf{Motivation:}
        Pangenome graphs provide a complete representation of the mutual alignment of
        collections of genomes. These models, therefore, offer the opportunity to study the entire genetic diversity of
        a population, bringing new challenges to how to analyze hundreds of genomes on a gigabase scale. In addition,
        vertebrate genomes present highly repetitive regions which increase the complexity of the analysis.
        Efficient and flexible tools are therefore required to work on pangenome graphs of any complexity and scale.\\
        \textbf{Results:} Here we present ODGI, a new suite of tools to analyze and manipulate pangenome graphs
        structured in the variation graph model. ODGI supports graphs in the Graphical Fragment Assembly format version
        1 (GFAv1). The tools scale efficiently to large collections of eukaryotic genomes, allowing users to work easily
        with pangenome graphs of tens to thousands of large genomes while maintaining fast execution runtime and low
        memory overhead.\\
        \textbf{Availability:} ODGI is written in C++. Source code and user manual are freely available at
        \href{https://github.com/pangenome/odgi}{https://github.com/pangenome/odgi}.\\
        \textbf{Contact:}
        \href{andreaguarracino@outlook.com}{andreaguarracino@outlook.com},
        \href{erik.garrison@gmail.com}{erik.garrison@gmail.com}\\
        \textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics} online.}
    \maketitle

>>>>

\documentclass{bioinfo}

\usepackage{relsize} % for Cpp
\usepackage{xspace} % for Cpp

\newcommand{\odgi}{ODGI}
\newcommand{\cmd}[1]{{\texttt{#1}}}
\newcommand{\Rplus}{\protect\hspace{-.1em}\protect\raisebox{.35ex}{\smaller{\smaller\textbf{+}}}}
\newcommand{\pp}{\Rplus\Rplus}
\newcommand{\Cpp}{\mbox{C\Rplus\Rplus}\xspace}

\copyrightyear{2021} \pubyear{2021}

@@

    \title[short Title]{ODGI: scalable tools for pangenome graphs}
    \author[Sample \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2}}$,
        % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}*}$
    }
    \address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 2}}$Department, Institution, City, Post Code, Country \\
        $^{\text{\sf 3}}$Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }

@@

    \abstract{ \textbf{Motivation:} Pangenome graphs provide a
      complete and `lossless' representation of genomic information
      that allows for complex population-sized analysis of genomes
      without introducing reference genome bias. Here we present a
      range of novel tools that makes use of the \odgi\ efficient
      in-memory representation of DNA/RNA graphs. \odgi\ can handle
      thousands of large genomes while maintaining fast execution
      runtime and low memory overhead. \odgi\ includes tools for
      detecting complex regions, extracting loci, exploratory
      analysis, sorting, removing artifacts and visualisation.
      %
      \\
      \textbf{Availability:} \odgi\ is software written in the \Cpp\
      programming language and published under the libre MIT license. Source
      code and user manual can be downloaded from
      \href{https://github.com/pangenome/odgi}{https://github.com/pangenome/odgi}.\\
      %
        \textbf{Contact:}
        \href{andreaguarracino@outlook.com}{andreaguarracino@outlook.com},
        \href{erik.garrison@gmail.com}{erik.garrison@gmail.com}\\ \textbf{Supplementary
          information:} Supplementary data are available at
        \textit{Bioinformatics} online.}

    \maketitle
